Spectroscopic confirmation of very-wide stellar binaries and large-separation comoving pairs from \textsl{Gaia DR1}

### 2017-07-28 paper/comoving-followup.tex
abstract

\title{Spectroscopic confirmation of very-wide binaries and large-separation
       comoving pairs from \textsl{Gaia DR1}}

@@

\begin{abstract}
% Context
Widely-separated ($\gtrsim 0.1$~pc), coeval stars are powerful tools for
testing star-formation model predictions, improving stellar atmosphere models,
and inferring the mass distribution of the Milky Way.
They likely outnumber the Galactic open clusters by a large margin, but are
still expected to share a common origin and chemistry.
The kinematic properties of comoving pairs---including bound wide binaries---
serve as potentiometers for the smooth tidal field and mass perturbation
spectrum of the Milky Way.
Thus far, a few hundred confirmed comoving star pairs with separations as large
as $8~\pc$ have been discovered in the solar neighborhood using
\project{Hipparcos}.
% Aims
In previous work, we have identified $\sim 4,000$ candidate comoving star pairs
using only astrometric data from the Tycho-Gaia Astrometric Solution (TGAS)
catalog, a part of \gaia\ \DR{1}.
Without radial velocity measurements for the vast majority of the pairs, the
false-positive rate at large separations is significant ($\sim 50\%$).
% Methods
Here, we present results from our own low-resolution radial-velocity survey of a
sample of the candidate pairs to validate wide-separation comoving star pairs.
% Results
Of the \npairsobs\ observed comoving pairs, we confirm \ncomoving\ comoving
pairs with separations as large as $\approx 10~\pc$, our original search limit.
% Conclusions
We find that the number of comoving star pairs with very wide separations
appears flat in linear separation at separations $\gtrsim 1~\pc$, strongly
suggesting the existence of a population of recently unbound wide binaries or
stellar associations.
% Gaia DR2 -> how many do we expect? Can we say anything? Out to what distance and
% separation for a typical MS star can we determine they are bound assuming
% high-res spectra to get very precise RVs?
\end{abstract}

>>>>

\title{Spectroscopic confirmation of very-wide stellar binaries and
       large-separation comoving pairs from \textsl{Gaia DR1}}

@@

\begin{abstract}
% Context
Members of widely-separated stellar binaries ($\gtrsim 0.1$~pc) or loosely bound
stellar associations and clusters are born with small spreads in kinematics and
chemistry, but disrupt and dissociate on timescales comparable to their orbital
time within the Milky Way.
The kinematic properties of comoving star pairs---bound wide binaries or unbound
but coeval stars---are therefore sensitive to both the smooth tidal field and
mass perturbation spectrum of the Milky Way.
% Aims
% Thus far, a few hundred confirmed comoving pairs with separations as large as
% $8~\pc$ have been discovered in the solar neighborhood using
% \project{Hipparcos} astrometry combined with radial velocity surveys.
In previous work, we identified $>4,000$ candidate comoving pairs using only
astrometric data from the Tycho-Gaia Astrometric Solution (TGAS) catalog and
find an abundance of pairs at separations $\gtrsim 1~\pc$.
Without radial velocity measurements for the vast majority of these pairs, the
false-positive rate at these separations is significant ($\sim 50\%$).
% Methods
Here, we present results from our own low-resolution radial-velocity survey of a
random sample of the candidate pairs to identify and validate true comoving star
pairs.
% Results
Of the \npairsobs\ observed comoving pairs, we confirm \ncomoving\ comoving
pairs with separations as large as $\approx 10~\pc$, our original search limit.
From the smallest separation pairs, $\approx 10^{-3}~\pc$, out to $\approx
0.5~\pc$, we find that the number of confirmed comoving star pairs decreases
with increasing separation, as expected.
From $\approx 0.5~\pc$ to $10~\pc$, the separation distribution appears
approximately uniform.
% Conclusions
We therefore confirm the discovery of a population of comoving star pairs at
very large separations, strongly suggesting an abundance of disrupted wide
binaries and stellar associations in the Galactic disk.
\end{abstract}

% The confirmed discovery of this population of coeval, comoving stars will
% enable future dynamical tests of dark matter and XX of star formation XX.
% as predicted from simulations of the disruption and evolution of wide binary
% stars. Gaia DR2 -> how many do we expect? Can we say anything? Out to what
% distance and separation for a typical MS star can we determine they are bound
% assuming high-res spectra to get very precise RVs?
